\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage[T1]{fontenc}
\pdfgentounicode=1

% Adjust margins (middle ground)
\addtolength{\oddsidemargin}{-0.625in}
\addtolength{\evensidemargin}{-0.625in}
\addtolength{\textwidth}{1.25in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item[\textopenbullet]\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
    \textit{\small#5} & \textit{\small #6} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, label=\textopenbullet]} 
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%---------- HEADING ----------
\begin{center}
  \textbf{\Huge \scshape Austyn Nguyen} \\ \vspace{3pt}
  \small
  \faEnvelope \hspace{.5pt} \href{mailto:austynan@umich.edu}{austynan@umich.edu}
  $|$
  \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/austyn-an-nguyen}{linkedin.com/in/austyn-an-nguyen}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/austyn-nguyen}{github.com/austyn-nguyen}
  $|$
  \faMapMarker \hspace{.5pt} Ann Arbor, MI
\end{center}

%----------- EDUCATION -----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of Michigan -- Ann Arbor}{Ann Arbor, MI}
  {B.S.E. in Computer Science, B.S. in Economics; Minor in Entrepreneurship; \textbf{GPA: 3.41/4.00}}{Apr. 2028}
  \resumeItemListStart
    \resumeItem{Coursework: Data Structures/Algorithms, Computer Organization, Digital Logic Design, Probability \& Statistics}
    \resumeItem{Study Abroad: Yonsei University, Seoul, South Korea}
\resumeItemListEnd

  \resumeSubheading
    {Howard Community College}{Columbia, MD}
    {A.A. in Computer Science, A.A. in General Studies (STEM); \textbf{GPA: 4.00/4.00}}{May 2024}
    \resumeItemListStart
        \resumeItem{Honors: Phi Theta Kappa, Frederick K. Schoenbrodt Scholar, Summa Cum Laude}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- SKILLS & TECHNICAL TOOLS -----------
\section{Skills \& Technical Tools}
\resumeSubHeadingListStart
  \item{
    \textbf{Languages:} Python, Java, C, C++, Assembly, Verilog, SQL, MATLAB, JavaScript, HTML/CSS \\
    \textbf{Technologies:} Git, Power BI, PowerApps, Power Automate, Azure, Fabric, DevOps, SharePoint, Excel, Pandas, Numpy, Matplotlib, Jupyter, Linux, MacOS, Windows
  }
\resumeSubHeadingListEnd

%----------- EXPERIENCE -----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {The Chemours Company}{Wilmington, DE}
    {Data Analyst Intern}{May 2025 -- Present}
    \resumeItemListStart
      \resumeItem{Designed and deployed interactive dashboards in Power BI and SQL to surface trends in S\&P Global trade data, directly supporting strategic decision-making across supply chain and commercial teams.}
      \resumeItem{Collaborated cross-functionally with business leaders to align KPIs with trade strategy, applying data modeling and DAX to drive actionable insights that informed key planning processes.}
      \resumeItem{Spearheaded integration of Git with Power BI and DevOps workflows; led training sessions that institutionalized analytics' best practices across business and IT units.}
    \resumeItemListEnd

  \resumeSubheading
  {Michigan Medicine: Watson Lab}{Ann Arbor, MI}
  {Data Engineer}{Jan. 2025 -- May 2025}
  \resumeItemListStart
    \resumeItem{Translated complex neural signal processing tasks into streamlined, reusable shell and MATLAB scripts—empowering PhD researchers to handle large-scale data without deep coding knowledge.}
    \resumeItem{Leveraged the open-source Spike2 API to organize 60-channel, 48-hour recordings (2TB+ of electrophysiological data) into structured, reproducible formats—streamlining team workflows and enabling scalable downstream analysis and visualization across neuroscience collaborators.}
  \resumeItemListEnd

\resumeSubheading
  {National Institute of Standards and Technology (NIST)}{Gaithersburg, MD}
  {Software Engineering Intern}{May 2024 -- Aug. 2024}
  \resumeItemListStart
    \resumeItem{Designed and implemented an automated result submission framework using GitHub Actions, streamlining processing of 8+ benchmark results and automating validation with 100\% accuracy to reduce manual effort and accelerate workflows.}
    \resumeItem{Deployed Git LFS to efficiently manage and store a 512+ GB dataset supporting 200+ phase field simulations, ensuring reliable data accessibility for research teams.}
    \resumeItem{Presented technical workflows and automation solutions to interdisciplinary research symposium, effectively communicating complex processes to diverse scientific audiences.}

  \resumeItemListEnd


\resumeSubHeadingListEnd

%----------- PROJECTS -----------
%----------- ACTIVITIES & LEADERSHIP -----------
\section{Activities \& Leadership}
\resumeSubHeadingListStart

  \resumeSubheading
    {Zeta Pi Technical Fraternity}{Ann Arbor, MI}
    {Member at Large}{Jan. 2025 -- Present}
    \resumeItemListStart
      \resumeItem{Conducted candidate interviews and membership deliberations to ensure a fair, thorough recruitment process.}
      \resumeItem{Led resume workshops to support members’ professional development, improving their career readiness skills.}
    \resumeItemListEnd

  \resumeSubheading
    {Michigan Pops Orchestra}{Ann Arbor, MI}
    {Assistant Principal Violist}{Jan. 2025 -- Present}
    \resumeItemListStart
      \resumeItem{Led viola sectionals to improve technique, rhythm, and musical cohesion.}
      \resumeItem{Engaged with Principal Violist and conductor to ensure section unity and dynamic balance across performances.}
    \resumeItemListEnd

    \resumeSubheading
    {UM Autonomous Robotic Vehicles (UMARV)}{Ann Arbor, MI}
    {Business Analyst}{Sep. 2024 -- Dec. 2024}
    \resumeItemListStart
      \resumeItem{Managed digital marketing across Instagram, LinkedIn, and X to boost engagement and visibility}
      \resumeItem{Coordinated sponsor outreach and events to support club initiatives and member opportunities}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}